---
title: Concept definition for manuscript
author: JM Delgado
date: February 1, 2019
output:
  pdf_document:
    footer: "University of Potsdam, Hydrology and Climatology, 2019"

---

# Aim

* Validate watermasks wherever possible
* Quantify variation of water availability for CE regions and whole state
* Compare with meteorological indeces like SPI
---

# Methods

1. Preprocessing
        * clean up GSWE dataset from Pekel et al. XXXX. Possibly use Till's filtered dataset.
        * prepare psql database for storing all watermasks
        * fetch sentinel-1 scenes for a period of 12 days (minimum for covering domain with at least one scene) every three months starting in October (October, January, April, July)
2. Watermasks
        * correct, calibrate, speckle filter etc.
        * subset scenes based on JRC dataset
        * threshold subsets
        * polygonize
        * store in database

3. Estimate stored volume
        * select approach for estimating HAV curve: by default 1c from Pereira et al. 2019
        * apply HAV curve to current watermask

# Preprocessing
```{r child = 'notebooks/01_manuscript_preprocessing.Rmd'}
```


# Estimate stored volume
```{r child = 'notebooks/03_manuscript_HAV.Rmd'}
```
