---
title: Large scale monitoring of reservoirs from space
author: JM Delgado
date: February 1, 2019
output: slidy_presentation
---

```{r echo=FALSE,warning=FALSE, message=FALSE,results='hide',include=FALSE}
library(sf)
library(dplyr)
library(ggplot2)

dataset = st_read('/home/delgado/proj/buhayra/notebooks/time-series-2019-02-11.geojson')
dataset_sf = dataset %>% as_data_frame
st_geometry(dataset) = NULL
dataset %>% head

ref = st_read('/home/delgado/proj/buhayra/buhayra/auxdata/wm_utm_simplf.gpkg')
ref_ds = ref %>% mutate(ref_area=st_area(ref)) %>% rename(id_jrc=id)
ref_ll = ref %>% st_transform(.,crs=4326)
st_geometry(ref_ds) = NULL

watermasks = dataset %>%
  select(id_jrc,ingestion_time,area,wmxjrc_area) %>%
  left_join(.,ref_ds)

theme_set(theme_gray(base_size = 18))
```

---

# Aim

* Detection of water surface of reservoirs with SAR imagery from the sentinel mission.
* Derive time series of water availability for each reservoir

---

# Method

* fetch sentinel-1 scenes
* correct, calibrate, speckle filter etc.
* subset scenes based on JRC dataset
* threshold subsets
* polygonize
* store in database

Go to the [buhayra repo](https://github.com/jmigueldelgado/buhayra#buhayra) for more details

---

# Results
 <!-- ids = watermasks %>% select(id_jrc,wmxjrc_area,area,ref_area) %>% filter(wmxjrc_area>0) %>% group_by(id_jrc) %>% summarise(id=first(id_jrc),wmxjrc_index=mean(wmxjrc_area/area)) %>% filter(wmxjrc_index>0.5) %>% .$id %>% sample(.,10) -->

* [leaflet visualization](http://141.89.96.184/index.html)
* some plots in this presentation

---

## Time series of water extent

```{r echo=FALSE,warning=FALSE,message=FALSE}
ids = c(5402,6821,6547,2194,6520,5469)

watermasks %>% filter(id_jrc %in% ids) %>%
  group_by(id_jrc) %>%
  mutate(area_index = area/ref_area) %>%
  filter(area_index<3) %>%
  ggplot + geom_point(aes(x=ingestion_time,y=area_index)) + facet_wrap(id_jrc~.)
```

---

## Time series continued
```{r echo=FALSE,warning=FALSE,message=FALSE}
ids=c(3555,4181,5918,5463,3040,265,2689)
watermasks %>% filter(id_jrc %in% ids) %>%
  group_by(id_jrc) %>%
  mutate(area_index = area/ref_area) %>%
  filter(area_index<3) %>%
  ggplot + geom_point(aes(x=ingestion_time,y=area_index)) + facet_wrap(id_jrc~.)
```

---

## Example 1

```{r echo=FALSE,warning=FALSE,message=FALSE}
ID = 6821
dataset_sf %>%
  filter(id_jrc==ID) %>%
  filter(area>0) %>%
  arrange(ingestion_time) %>%
  ggplot(.) +
  geom_sf() +
  geom_sf(data=filter(ref_ll,id==ID),fill=NA,color='orange') +
  facet_wrap(.~ingestion_time) +
  ggtitle(ID)
```

---

## Example 2

```{r echo=FALSE,warning=FALSE,message=FALSE}
ID = 5402
dataset_sf %>%
  filter(id_jrc==ID) %>%
  filter(area>0) %>%
  arrange(ingestion_time) %>%
  ggplot(.) +
  geom_sf() +
  geom_sf(data=filter(ref_ll,id==ID),fill=NA,color='orange') +
  facet_wrap(.~ingestion_time) +
  ggtitle(ID)
```

---

## Example 3

```{r echo=FALSE,warning=FALSE,message=FALSE}
ID = 265
dataset_sf %>%
  filter(id_jrc==ID) %>%
  filter(area>0) %>%
  arrange(ingestion_time) %>%
  ggplot(.) +
  geom_sf() +
  geom_sf(data=filter(ref_ll,id==ID),fill=NA,color='orange') +
  facet_wrap(.~ingestion_time) +
  ggtitle(ID)
```

---

## Example 4

```{r echo=FALSE,warning=FALSE,message=FALSE}
ID = 6547
dataset_sf %>%
  filter(id_jrc==ID) %>%
  filter(area>0) %>%
  arrange(ingestion_time) %>%
  ggplot(.) +
  geom_sf() +
  geom_sf(data=filter(ref_ll,id==ID),fill=NA,color='orange') +
  facet_wrap(.~ingestion_time) +
  ggtitle(ID)
```

---

## Example 5

```{r echo=FALSE,warning=FALSE,message=FALSE}
ID = 2194
dataset_sf %>%
  filter(id_jrc==ID) %>%
  filter(area>0) %>%
  arrange(ingestion_time) %>%
  ggplot(.) +
  geom_sf() +
  geom_sf(data=filter(ref_ll,id==ID),fill=NA,color='orange') +
  facet_wrap(.~ingestion_time) +
  ggtitle(ID)
```

---


## Example 6

```{r echo=FALSE,warning=FALSE,message=FALSE}
ID = 5918
dataset_sf %>%
  filter(id_jrc==ID) %>%
  filter(area>0) %>%
  arrange(ingestion_time) %>%
  ggplot(.) +
  geom_sf() +
  geom_sf(data=filter(ref_ll,id==ID),fill=NA,color='orange') +
  facet_wrap(.~ingestion_time) +
  ggtitle(ID)
```

---

# Further steps
* explain reservoirs of area zero
  - by cleaning threshold module
  - by implementing an assimilation approach like a Kalman filter
* integrate with tdx2hav
* vegetated areas?
